### 2018-11-28 chapters/3-results.tex
readability

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Both L1 and L2 regularization methods were
utilized separately. Table~\ref{tab:auc_imagetype} contains the results for
models within each image type using all or top 1\% of the features. The results
are AUC values with confidence intervals included.

@@

In contrast to L1, L2 regularization yielded better performance for all image
types except for T₂w where AUC dropped to 0.68. DWI derived parametric maps
(ADCₘ, ADCₖ, K) had AUC between 0.69 to 0.73, and T₂ derived features had
AUC=0.70.

>>>>

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Both L1 and L2 regularization methods were
utilized separately. Table~\ref{tab:auc_imagetype} contains the results for
models within each image type using all or top 1\% of the features. The results
are ROC AUC values with confidence intervals included.

@@

In contrast to L1, L2 regularization yielded better performance for all image
types except T₂w where AUC dropped to 0.68. DWI derived parametric maps (ADCₘ,
ADCₖ, K) had AUC between 0.69 to 0.73, and T₂ derived features had AUC=0.70.
